\documentclass[11pt]{article}
\usepackage{graphicx}
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage{lipsum}
\usepackage[left=1.06cm,top=1.7cm,right=1.06cm,bottom=0.49cm]{geometry}

\hypersetup{
    pdftitle={CV - Thomas Bermúdez Mora},
    pdfauthor={Thomas Bermúdez Mora}
}

\begin{document}
\begin{center}
    \textbf{THOMAS EMANUEL BERMÚDEZ MORA\\ }
    \hrulefill
\end{center}

\begin{center}
    \href{mailto:bmthomas.code@gmail.com}{bmthomas.code@gmail.com} \textbullet \ \href{https://wa.me/50662536365}{+506 6253 6365} \textbullet \ \href{https://www.linkedin.com/in/thomas-bermudez-mora/}{linkedin.com/in/thomas-bermudez-mora} \textbullet \ \href{https://thomasbm.com/}{thomasbm.com}
\end{center}

\vspace{0.5pt}

\begin{center}
    \textbf{Profile}
\end{center}

Full-stack software engineer specializing in web applications with a strong UI/UX focus and machine learning expertise in computer vision. Contributed to award-winning projects at Cannes Lions Festival and Grupo AUGE-UCR. Committed to craftsmanship, education, and continuous improvement.

\begin{center}
    \textbf{Experience}
\end{center}

\textbf{Link Agency} \hfill San José, Costa Rica / Remote

\textbf{Software Developer} \hfill Jun 2023 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Maintained and implemented WordPress sites, prioritizing responsive UI/UX across multiple client projects.
    \item Integrated custom PHP functionalities to reduce plugin dependencies and improve code maintainability.
    \item Optimized MySQL database structures for seamless integration with in-house server environments.
    \item Developed a website for a campaign that earned a Silver Lion at the 72nd Cannes Lions Festival.
    \item Served as primary developer for a custom web application that replaced Excel workflows, eliminated 100\% of manual data entry, automated work order processing, and enabled real-time tracking with visual reporting.
\end{itemize}

\vspace{10pt}

\textbf{ISAAC Project (Freelance for UCR undergraduates)} \hfill San José, Costa Rica / Remote

\textbf{Machine Learning \& Backend Developer} \hfill Mar 2023 – Nov 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Developed backend/ML infrastructure for the ISAAC Project, awarded by the 2022 Program of Technological Innovation (AUGE-UCR Group), enabling UCR students to graduate with honors based on project results.
    \item Generated and validated wildlife image datasets from camera trap data to train species classification models.
    \item Trained computer vision models in Python (Google Colab, TensorFlow/PyTorch), achieving 98.22\% test accuracy with only 11 errors out of 618 samples.
    \item Maintained precision scores exceeding 93\% for frequent classes with strong recall on challenging categories and robust handling of unseen species.
    \item Designed MySQL database structures for project, user, and species data management.
    \item Implemented Flask REST APIs for authentication, project management, and species reclassification workflows.
    \item Deployed system to AWS with cost-optimized architecture, balancing performance and operational expenses.
\end{itemize}

\vspace{10pt}

\textbf{MobyDyg} \hfill Heredia, Costa Rica / Remote

\textbf{Full-stack Software Engineer} \hfill Mar 2022 – Nov 2022
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Designed and implemented a user management system for e-commerce staff portals using Angular, TypeScript, SCSS, and AWS Cognito, integrating responsive front-end modules with AWS Amplify and SDK for secure authentication and role-based access control.
    \item Rebuilt, normalized and migrated the company's MySQL database, ensuring compliance with relational best practices and improving query efficiency, data integrity, and security.
    \item Collaborated in team-based and pair programming environments to accelerate feature delivery and improve code quality.
\end{itemize}

\vspace{10pt}

\textbf{Cenfotec University} \hfill San José, Costa Rica / Remote

\textbf{Machine Learning \& Computer Vision Intern} \hfill Jan 2022 – Dec 2025
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Developed an ALPR system using YOLOv5, Flask API, and Google Colab, achieving 96\% accuracy in license plate detection and 77\% in vehicle detection.
    \item Web scraped an experimental dataset of 942 Costa Rican license plates to improve local model performance.
    \item Implemented a multi-stage detection pipeline with OCR preprocessing to enhance text recognition accuracy.
    \item Built and deployed a cloud-based API service for image uploads, detection processing, and plate text extraction.
    \item Authored an academic research paper detailing methodology, experimental results, and recommendations for system optimization.
\end{itemize}

\vspace{10pt}

\textbf{3Pillar Global} \hfill San José, Costa Rica / Remote

\textbf{Software Engineering Intern} \hfill Oct 2021 – Jan 2022
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Prototyped responsive web application interfaces in Figma and implemented them with React.js, ensuring consistency with the client's design system.
    \item Designed SQL Server database and implemented backend features using C\# and ASP.NET MVC for maintainability and scalability.
    \item Collaborated through pair programming and code reviews to validate functionality and improve code quality.
\end{itemize}

\vspace{10pt}


\begin{center}
    \textbf{Education}
\end{center}
\textbf{Cenfotec University} \hfill San José, Costa Rica

Bachelor of Software Engineering. GPA 4.0 \hfill Jan 2022 - Dec 2025

Honors: Holder of a 100\% scholarship for academic excellence.

\vspace{10pt}

\textbf{Cenfotec University} \hfill San José, Costa Rica

Machine Learning with Python \hfill Nov 2022 - Dec 2022

\vspace{10pt}


\begin{center}
    \textbf{Skills}
\end{center}

\textbf{Technical:} Python, JavaScript, TypeScript, PHP, C\#, HTML, CSS/SCSS • React.js, Angular, Flask • MySQL, SQL Server • WordPress • AWS • TensorFlow, YOLO, Google Colab • Git, GitHub • Figma

\textbf{Soft:} Empathy, Resilience, Self-Control, Adaptability

\textbf{Languages:} Spanish (Native), English (C1 - TOEFL iBT)

\vspace{10pt}

\begin{center}
    \textbf{Extracurricular Activities}
\end{center}

\textbf{Robotics \& Programming Instructor} \hfill The ClubHouse, CEDES Don Bosco

Volunteer educator teaching robotics fundamentals and programming concepts to children, fostering early interest in STEM and computational thinking. \hfill Sep 2025 – Present


\end{document}
